Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-02 paper_review/response_20200826.txt

******************************************
REFEREE COMMENT
----------
Sec. 3.1.3
The outer separation of the "Not SB2" constraint in the top panel
of Fig. 6 seems optimistic. Wouldn't the velocity separation of a
binary with a=100 AU be less than the broadening of 15 km/s?

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
Sec. 3.1.4
It is not clear how the range of K-P parameter space stated was
explored in detail. MCMC sampling is inefficient for multimodal
distributions, and given the sparse sampling of the RV time
series, it seems likely that multiple modes exist. Was K fit
independently over a grid of periods? Orbital inclination would
also be an important parameter to include. If models were used to
transform mass ratio limits to contrast limits this should be
explicitly stated.

RESPONSE
----------
> Prompted by this comment, we have amended our method for sampling
> K-P parameter space to one that we feel is more robust against
> inefficient sampling and the multimodal nature of the long-period
> detection problem. The last paragraph of Section 3.1.4 has been
> amended to the following:
>
> """
> We performed the following injection-recovery exercise.  We
> simulated $10^6$ two-body systems with random orbital phases and
> inclinations, and semi-amplitudes and periods drawn from logarithmic
> distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
> and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
> assuming circular orbits, we then analytically evaluated what the
> radial velocities would have been at the observed FEROS times if the
> system had the assumed parameters.  We then calculated what the
> linear slope would have been for each simulated system.  If the
> absolute value of the slope exceeded our 3-$\sigma$ limit of
> $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we
> assumed that we would have detected such a system.
> Figure~\ref{fig:fpscenario} shows the resulting detection limits;
> weakened sensitivity at harmonics of the baseline occur at lower
> masses and smaller projected separations than shown on the plot.
> The conversion from mass to brightness contrast was performed using
> the same 35 Myr MIST isochrones and assumptions as in Section 3.1.2.
> """
>
> As a supplement for the referee's inspection, we also attach a plot
> showing the simulated "detections" and "non-detections" directly in
> the Msini vs semi-major axis plane (yellow points are detected;
> purple are not).

### 2020-09-02 paper/ms.tex
address comments on RV limits
better method for {semi-amplitude, period} constraints based on no RV
trend.

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.75\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
    companions along the same line of sight (BEB scenarios).  Each
    constraint is described in Section~\ref{subsec:fp_constraints}.
    Gray regions are ruled out by at least one constraint.
		\label{fig:fpscenario}
	}
\end{figure*}

@@

\subsubsection{Speckle Imaging}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
bound companions, we used the \citet{baraffe_evolutionary_2003} models
for sub-stellar mass objects and the MIST models for stellar mass
objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, so that companions would be
at a plausible state of contraction.

@@

\subsubsection{RVs}
The radial velocities from FEROS, CHIRON, and Veloce can be used to
detect massive bound companions orbiting \tn.  We searched for the
presence of planetary and stellar-mass companions using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits, and performed two sets of fits.

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit we set a prior on the period and time of conjunction
using the known ephemeris from the transit.  We then fitted for the
semi-amplitude, instrument offsets, and jitter parameters.  This
yielded a non-detection of the planet's orbit.  The corresponding
3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on $M_{\rm p} \sin
i$ is $1.20 M_{\rm Jup}$.  The data and corresponding model are shown
in Figure~\ref{fig:rvs}.

@@

To place limits on the properties of a possible bound hierarchical
companion, we fitted the radial velocity data for a Keplerian orbit
assuming wide logarithmic priors on the semi-amplitude and period: $K\
[{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}]
\sim \log \mathcal{U}(0.1, 10^{15})$.  We then fitted for the
semi-amplitude, period, time of conjunction, instrument offsets, and
jitter parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.75\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
    companions along the same line of sight (BEB scenarios).  Each
    constraint is described in Section~\ref{subsec:fp_constraints}.
    Gray regions are ruled out by at least one constraint.
		\label{fig:fpscenario}
	}
\end{figure*}

@@

\subsubsection{Speckle Imaging}
\label{subsec:speckleconstraint}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
bound companions, we used the \citet{baraffe_evolutionary_2003} models
for sub-stellar mass objects and the MIST models for stellar mass
objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, so that companions would be
at a plausible state of contraction.

@@

\subsubsection{RVs}
The radial velocities from FEROS, CHIRON, and Veloce can be used to
detect massive bound companions orbiting \tn.  We searched for the
presence of planetary and stellar-mass companions \replaced{using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits, and performed two sets of fits}{in two different regimes:
first, at the orbital period of the transiting object, and second, at
longer orbital periods to constrain the presence of a massive bound
companion. }.

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit we set a prior on the period and time of conjunction
using the known ephemeris from the transit.  We then fitted for the
semi-amplitude, instrument offsets, and jitter parameters \added{using
\texttt{radvel} \citep{fulton_radvel_2018}, and assuming circular
orbits}.  This yielded a non-detection of the planet's orbit.  The
corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
model are shown in Figure~\ref{fig:rvs}.

@@

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and semi-amplitudes and periods drawn from logarithmic
distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
assuming circular orbits, we then analytically evaluated what the
radial velocities would have been at the observed FEROS times if the
system had the assumed parameters.  We then calculated what the linear
slope would have been for each simulated system.  If the absolute
value of the slope exceeded our 3-$\sigma$ limit, we assumed that we
would have detected such a system.  Figure~\ref{fig:fpscenario} shows
the resulting detection limits; weakened sensitivity at harmonics of
the baseline occur at lower masses and smaller projected separations
than shown on the plot. The conversion from mass to brightness
contrast was performed using the same 35 Myr MIST isochrones and
assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}
